---
title: "Storm Data Shiny App"
author: "Bhawna G. Panwar"
date: "Sunday, September 21, 2014"
output: html_document
---

## Motivation

Storms affect all US states. It would be nice to have an app that can quickly tell us which kinds of storms are worst in which states and how damaging they are.  This app addresses that in a click of a button.

```{r}

```

---
## Description

This storm data app provides an interactive and easy way to plot the most damaging weather events in the USA by state.  It is derived from the NOAA historical storm events database.

## Target Audience

Anyone who is curious about storm impacts in various states, plus governments who want to prepare for the most impactful events.

```{r, echo=FALSE}

```
---
## App Layout and Usage

The Storm Data Shiny App is simple and very easy to use.

## How it works

The user simply selects the state in the UI and the app provides a plot of the ten most damaging event types in that state with their respective damage to property.

---
## Sample Output (for Texas)

```{r, echo=FALSE}
stormdata <- read.table("total.cost.bystate.txt", header=T, sep = ",")

# Get the top ten most costly weather events for the input state
stateData <- stormdata[stormdata$STATE == 'TX',]
top10 <- stateData[order(-stateData$PROPDMG),][1:10,]
    
plot1 <- ggplot(data=top10, aes(x=reorder(EVTYPE,PROPDMG), y=PROPDMG)) + geom_bar(stat="identity",color="cyan") + coord_flip() + 
  ggtitle("Total Property Damage due to Event Type ") + xlab("Top Ten Event Type") + ylab("Cost amount in Dollars")
print(plot1)
```
